---
title: 'The Morale Effects of Pay Inequality (Breza, Kaur, and Shamdasani)'
author: "R Replication Code for Table V and Table A.II by Yuen Ho"
date: "4/5/2021"
header-includes:
  - \usepackage{float}
  - \floatplacement{figure}{H}
  - \usepackage{amsmath}
  - \usepackage{caption}
  - \captionsetup[table]{labelformat = empty}
output: pdf_document
fig_caption: No
geometry: margin = 1.5cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#==================
# Section 0: Set Up
#==================

# Clear workspace
rm(list = ls())

# Load packages
library(pacman)
p_load(zoo, haven, data.table, dplyr, foreign, tidyr, xtable, broom, stringr, ggplot2, plm, lmtest, sandwich, stargazer, miceadds, multiwayvcov)

# Directory
# Set working directory
base_directory <- "/Users/yuen/Documents/GitHub/RevisedMoraleEffects/"

# read data
final <- as.data.table(read_dta(paste0(base_directory, "finaldataset.dta")))
el_games1 <- as.data.table(read_dta(paste0(base_directory, "el_games1.dta")))
el_games2 <- as.data.table(read_dta(paste0(base_directory, "el_games2.dta")))

# Convert relevant variables into factor variables
final[,task_id := as.factor(task_id)]
final[,day_round := as.factor(day_round)]
final[, team_id := as.factor(team_id)]

## Create variable vectors
# Vector with all neighbor controls
neighbor_all <- final %>% select(starts_with("neighbor"))
neighbor_all <- colnames(neighbor_all)

# Vector with neighbor post no treatment controls
neighbor_post_noT <- final %>% select(starts_with("neighbor_pn_"))
neighbor_post_noT <- colnames(neighbor_post_noT)

# Vector with all neighbor post controls
neighbor_post <- final %>% select(starts_with("neighbor_pt_"))
neighbor_post <- colnames(neighbor_post)

# Vector with all linear experience task controls
exper_task_lin <- final %>% select(starts_with("exper_task_lin"))
exper_task_lin <- colnames(exper_task_lin)

# Vector with squared experience task controls
exper_task_sq <- final %>% select(starts_with("exper_task_sq"))
exper_task_sq <- colnames(exper_task_sq)

# Vector with neighbor pre - low controls
neighbor_pre_l <- final %>% select(starts_with("neighbor_l"))
neighbor_pre_l <- colnames(neighbor_pre_l)

# Vector with neighbor pre - med controls
neighbor_pre_m <- final %>% select(starts_with("neighbor_m"))
neighbor_pre_m <- colnames(neighbor_pre_m)

# Vector with neighbor pre - high controls
neighbor_pre_h <- final %>% select(starts_with("neighbor_h"))
neighbor_pre_h <- colnames(neighbor_pre_h)
```

```{r Table 4, results = 'asis', echo = FALSE, fig.align = "center", out.width = 4, out.height = 4, warning = FALSE}
#==================================
# Table 4: Effects of Pay Disparity
#==================================
### Panel A: Pooled Treatment Effects
## Without FE
x <- c("posttreat", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", "low_p", "med_p", "high_p", "treatlow", "treatmed", "treathigh", "irrellow", "irrelmed", "irrelhigh", "day_round", exper_task_lin, exper_task_sq, "task_id", neighbor_all)
x <- paste(x, collapse = "+")

# dependent variable = output
reg1 <- lm(formula(paste0("prodnorm", "~",x)), data = final)
vcov_teamid <- cluster.vcov(reg1, final$team_id)
reg1_cluster <- coeftest(reg1, vcov_teamid)

# dependent variable = attendance
reg2 <- lm(formula(paste0("attendance", "~", x)), data = final)
vcov_teamid <- cluster.vcov(reg2, final$team_id)
reg2_cluster <- coeftest(reg2, vcov_teamid)

## With FE
x <- c("posttreat", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", neighbor_post_noT, neighbor_post, "day_round", exper_task_lin, exper_task_sq)
x <- paste(x, collapse = "+")

# dependent variable = output
reg3 <- lm(formula(paste0("prodnorm","~",x,"+ factor(uid)")), data = final)
vcov_teamid <- cluster.vcov(reg3, final$team_id, stata_fe_model_rank = TRUE)
reg3_cluster <- coeftest(reg3, vcov_teamid)

# dependent variable = attendance
reg4 <- lm(formula(paste0("attendance","~",x,"+ factor(uid)")), data = final)
vcov_teamid <- cluster.vcov(reg4, final$team_id, stata_fe_model_rank = TRUE)
reg4_cluster <- coeftest(reg4, vcov_teamid)

# conditional on attendance - no FE
x <- c("posttreat", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", "low_p", "med_p", "high_p", "treatlow", "treatmed", "treathigh", "irrellow", "irrelmed", "irrelhigh", "day_round", exper_task_lin, exper_task_sq, "task_id", neighbor_all)
x <- paste(x, collapse = "+")

reg5 <- lm(formula(paste0("prodnorm", "~", x)), data=final[attendance == 1,])
vcov_teamid <- cluster.vcov(reg5, final[attendance == 1, team_id])
reg5_cluster <- coeftest(reg5, vcov_teamid)

# combine models into latex table
stargazer(reg1_cluster, reg2_cluster, reg3_cluster, reg4_cluster, reg5_cluster, type = "latex", keep = "posttreat", header = FALSE, title = "Table 4: Panel A", dep.var.caption = "", column.labels = c("Output", "Attendance", "Output", "Attendance", "Output|Att"), table.placement = "H", add.lines=list(c('Individual Fixed effects', 'No', 'No', 'Yes', 'Yes', 'No'), c('N','8,375','8,375','8,375','8,375','7.678')))

### Panel B: Treatment Effects Separately by Rank
## Without FE
x <- c("treatlowpost", "treatmedpost", "treathighpost", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", "low_p", "med_p", "high_p", "treatlow", "treatmed", "treathigh", "irrellow", "irrelmed", "irrelhigh", "day_round", exper_task_lin, exper_task_sq, "task_id", neighbor_all)
x <- paste(x, collapse = "+")

# dependent variable = output
reg6 <- lm(formula(paste0("prodnorm", "~",x)), data = final)
vcov_teamid <- cluster.vcov(reg6, final$team_id)
reg6_cluster <- coeftest(reg6, vcov_teamid)

# dependent variable = attendance
reg7 <- lm(formula(paste0("attendance", "~",x)), data = final)
vcov_teamid <- cluster.vcov(reg7, final$team_id)
reg7_cluster <- coeftest(reg7, vcov_teamid)

## With FE
x <- c("treatlowpost", "treatmedpost", "treathighpost", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", neighbor_post_noT, neighbor_post, "day_round", exper_task_lin, exper_task_sq)
x <- paste(x, collapse = "+")

# dependent variable = output
reg8 <- lm(formula(paste0("prodnorm","~",x,"+ factor(uid)")), data = final)
vcov_teamid <- cluster.vcov(reg8, final$team_id, stata_fe_model_rank = TRUE)
reg8_cluster <- coeftest(reg8, vcov_teamid)

# dependent variable = attendance
reg9 <- lm(formula(paste0("attendance","~",x,"+ factor(uid)")), data = final)
vcov_teamid <- cluster.vcov(reg9, final$team_id, stata_fe_model_rank = TRUE)
reg9_cluster <- coeftest(reg9, vcov_teamid)

# conditional on attendance - no FE
x <- c("treatlowpost", "treatmedpost", "treathighpost", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", "low_p", "med_p", "high_p", "treatlow", "treatmed", "treathigh", "irrellow", "irrelmed", "irrelhigh", "day_round", exper_task_lin, exper_task_sq, "task_id", neighbor_all)
x <- paste(x, collapse = "+")

reg10 <- lm(formula(paste0("prodnorm", "~", x)), data=final[attendance == 1,])
vcov_teamid <- cluster.vcov(reg10, final[attendance == 1, team_id])
reg10_cluster <- coeftest(reg10, vcov_teamid)

# Calculate post treatment compressed mean
mean_pt_prodnorm <- mean(final[post == 1 & Het == 0 & relevant == 1, prodnorm])
mean_pt_attendance <- mean(final[post == 1 & Het == 0 & relevant == 1, attendance])
mean_pt_attend_prodnorm <- mean(final[post == 1 & Het == 0 & relevant == 1 & attendance == 1, prodnorm])

# combine models into latex table
stargazer(reg6_cluster, reg7_cluster, reg8_cluster, reg9_cluster, reg10_cluster, type = "latex", keep = c("treatlowpost", "treatmedpost", "treathighpost"), header = FALSE, title = "Table 4: Panel B", dep.var.caption = "", column.labels = c("Output", "Attendance", "Output", "Attendance", "Output|Att"), table.placement = "H", add.lines=list(c('Individual Fixed effects', 'No', 'No', 'Yes', 'Yes', 'No'), c('N','8,375','8,375','8,375','8,375','7.678')))
```
The post treatment compressed mean for output is `r round(mean_pt_prodnorm,3)` standard deviations; for attendance is `r round(mean_pt_attendance,3)` standard deviations; and for output conditional on attendance is `r round(mean_pt_attend_prodnorm,3)` standard deviations.

\bigskip
\noindent
Note that the above code does not exactly replicate the clustered standard errors in the fixed effects models reported in the paper and in the original replication code provided in Stata. However, the clustered standard errors produced by this replication code are qualitatively comparable and are identical up to 2 decimal places. 

```{r Table A2, results = 'asis', echo = FALSE, fig.align = "center", out.width = 4, out.height = 4, warning = FALSE}
#===========================================================================
# Table A2: Effects of Pay Disparity: Robustness to Alternate specifications
#===========================================================================
### Panel A — Pooled Treatment Effects
## No irrelevant people, no neighbor controls
x <- c("posttreat", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", "day_round", exper_task_lin, exper_task_sq)
x <- paste(x, collapse = "+")

# outcome variable = output
rreg1p <- lm(formula(paste0("prodnorm","~",x,"+ factor(uid)")), data = final[relevant == 1,])
vcov_teamid <- cluster.vcov(rreg1p, final[relevant == 1, team_id], stata_fe_model_rank = TRUE)
rreg1p_cluster <- coeftest(rreg1p, vcov_teamid)

# outcome variable = attendance
rreg2p <- lm(formula(paste0("attendance","~",x,"+ factor(uid)")), data = final[relevant == 1,])
vcov_teamid <- cluster.vcov(rreg2p, final[relevant == 1,team_id], stata_fe_model_rank = TRUE)
rreg2p_cluster <- coeftest(rreg2p, vcov_teamid)

## No irrelevant people, add in neighbor controls
x <- c("posttreat", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", neighbor_post_noT, neighbor_post, "day_round", exper_task_lin, exper_task_sq)
x <- paste(x, collapse = "+")

# outcome variable = output
rreg3p <- lm(formula(paste0("prodnorm","~",x,"+ factor(uid)")), data = final[relevant == 1,])
vcov_teamid <- cluster.vcov(rreg3p, final[relevant == 1, team_id], stata_fe_model_rank = TRUE)
rreg3p_cluster <- coeftest(rreg3p, vcov_teamid)

# outcome variable = attendance
rreg4p <- lm(formula(paste0("attendance","~",x,"+ factor(uid)")), data = final[relevant == 1,])
vcov_teamid <- cluster.vcov(rreg4p, final[relevant == 1, team_id], stata_fe_model_rank = TRUE)
rreg4p_cluster <- coeftest(rreg4p, vcov_teamid)

## Main specification
x <- c("posttreat", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", neighbor_post_noT, neighbor_post, "day_round", exper_task_lin, exper_task_sq)
x <- paste(x, collapse = "+")

# outcome variable = output
rreg5p <- lm(formula(paste0("prodnorm","~",x,"+ factor(uid)")), data = final)
vcov_teamid <- cluster.vcov(rreg5p, final$team_id, stata_fe_model_rank = TRUE)
rreg5p_cluster <- coeftest(rreg5p, vcov_teamid)

# outcome variable = attendance
rreg6p <- lm(formula(paste0("attendance","~",x,"+ factor(uid)")), data = final)
vcov_teamid <- cluster.vcov(rreg6p, final$team_id, stata_fe_model_rank = TRUE)
rreg6p_cluster <- coeftest(rreg6p, vcov_teamid)

## Post period only: Add baseline controls for production and attendance
# outcome variable = output
x <- c("posttreat", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", "day_round", exper_task_lin, exper_task_sq, "baselineprod", "task_id", neighbor_pre_l, neighbor_pre_m, neighbor_pre_h)
x <- paste(x, collapse = "+")

rreg7p <- lm(formula(paste0("prodnorm","~",x)), data = final[day_centered >= 0,])
vcov_teamid <- cluster.vcov(rreg7p, final[day_centered >= 0, team_id], stata_fe_model_rank = TRUE)
rreg7p_cluster <- coeftest(rreg7p, vcov_teamid)

# outcome variable = attendance
x <- c("posttreat", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", "day_round", exper_task_lin, exper_task_sq, "baselineatt", "task_id", neighbor_pre_l, neighbor_pre_m, neighbor_pre_h)
x <- paste(x, collapse = "+")

rreg8p <- lm(formula(paste0("attendance","~",x)), data = final[day_centered >= 0,])
vcov_teamid <- cluster.vcov(rreg8p, final[day_centered >= 0, team_id], stata_fe_model_rank = TRUE)
rreg8p_cluster <- coeftest(rreg8p, vcov_teamid)

# combine models into latex table
stargazer(rreg1p_cluster, rreg2p_cluster, rreg3p_cluster, rreg4p_cluster, rreg5p_cluster, rreg6p_cluster, rreg7p_cluster, rreg8p_cluster, type = "latex", keep = c("posttreat"), header = FALSE, title = "Table A2: Panel A", dep.var.caption = "", column.labels = c("Output", "Attendance", "Output", "Attendance", "Output", "Attendance", "Output", "Attendance"), table.placement = "H", add.lines=list(c('Sample', 'Relevant', 'Relevant', 'Relevant', 'Relevant', 'Full','Full','Full','Full'), c('Pre-trmt obs','Yes','Yes','Yes','Yes','Yes','Yes','No','No'), c('Neighbor ctrls','No', 'No', 'Yes', 'Yes', 'Yes','Yes','Yes','Yes'), c('Individual FEs', 'Yes', 'Yes', 'Yes', 'Yes', 'Yes','Yes','No','No'), c('N','4,307','4,307','4,307','4,307','8,375','8.375','5,283','5,283')))

### Panel B — Treatment Effects Separately by Rank
## No irrelevant people, no neighbor controls
x <- c("treatlowpost", "treatmedpost", "treathighpost", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", "day_round", exper_task_lin, exper_task_sq)
x <- paste(x, collapse = "+")

# outcome variable = output
rreg1 <- lm(formula(paste0("prodnorm","~",x,"+ factor(uid)")), data = final[relevant == 1,])
vcov_teamid <- cluster.vcov(rreg1, final[relevant == 1, team_id], stata_fe_model_rank = TRUE)
rreg1_cluster <- coeftest(rreg1, vcov_teamid)

# outcome variable = attendance
rreg2 <- lm(formula(paste0("attendance","~",x,"+ factor(uid)")), data = final[relevant == 1,])
vcov_teamid <- cluster.vcov(rreg2, final[relevant == 1, team_id], stata_fe_model_rank = TRUE)
rreg2_cluster <- coeftest(rreg2, vcov_teamid)

## No irrelevant people, add in neighbor controls
x <- c("treatlowpost", "treatmedpost", "treathighpost", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", neighbor_post_noT, neighbor_post, "day_round", exper_task_lin, exper_task_sq)
x <- paste(x, collapse = "+")

# outcome variable = output
rreg3 <- lm(formula(paste0("prodnorm","~",x,"+ factor(uid)")), data = final[relevant == 1,])
vcov_teamid <- cluster.vcov(rreg3, final[relevant == 1, team_id], stata_fe_model_rank = TRUE)
rreg3_cluster <- coeftest(rreg3, vcov_teamid)

# outcome variable = attendance
rreg4 <- lm(formula(paste0("attendance","~",x,"+ factor(uid)")), data = final[relevant == 1,])
vcov_teamid <- cluster.vcov(rreg4, final[relevant == 1, team_id], stata_fe_model_rank = TRUE)
rreg4_cluster <- coeftest(rreg4, vcov_teamid)

## Main specification
x <- c("treatlowpost", "treatmedpost", "treathighpost", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", neighbor_post_noT, neighbor_post, "day_round", exper_task_lin, exper_task_sq)
x <- paste(x, collapse = "+")

# outcome variable = output
rreg5 <- lm(formula(paste0("prodnorm","~",x,"+ factor(uid)")), data = final)
vcov_teamid <- cluster.vcov(rreg5, final$team_id, stata_fe_model_rank = TRUE)
rreg5_cluster <- coeftest(rreg5, vcov_teamid)

# outcome variable = attendance
rreg6 <- lm(formula(paste0("attendance","~",x,"+ factor(uid)")), data = final)
vcov_teamid <- cluster.vcov(rreg6, final$team_id, stata_fe_model_rank = TRUE)
rreg6_cluster <- coeftest(rreg6, vcov_teamid)

## Post period only: Add baseline controls for production and attendance
# outcome variable = output
x <- c("treatlowpost", "treatmedpost", "treathighpost", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", "day_round", exper_task_lin, exper_task_sq, "baselineprod", "task_id", neighbor_pre_l, neighbor_pre_m, neighbor_pre_h)
x <- paste(x, collapse = "+")

rreg7 <- lm(formula(paste0("prodnorm", "~",x)), data = final[day_centered >= 0,])
vcov_teamid <- cluster.vcov(rreg7, final[day_centered >= 0, team_id], stata_fe_model_rank = TRUE)
rreg7_cluster <- coeftest(rreg7, vcov_teamid)

# outcome variable = attendance
x <- c("treatlowpost", "treatmedpost", "treathighpost", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", "day_round", exper_task_lin, exper_task_sq, "baselineatt", "task_id", neighbor_pre_l, neighbor_pre_m, neighbor_pre_h)
x <- paste(x, collapse = "+")

rreg8 <- lm(formula(paste0("attendance", "~",x)), data = final[day_centered >= 0,])
vcov_teamid <- cluster.vcov(rreg8, final[day_centered >= 0, team_id], stata_fe_model_rank = TRUE)
rreg8_cluster <- coeftest(rreg8, vcov_teamid)

# Calculate post-treatment compressed mean
mean_pt_prodnorm <- mean(final[post == 1 & Het == 0 & relevant == 1, prodnorm])
mean_pt_attendance <- mean(final[post == 1 & Het == 0 & relevant == 1, attendance])

# combine models into latex table
stargazer(rreg1_cluster, rreg2_cluster, rreg3_cluster, rreg4_cluster, rreg5_cluster, rreg6_cluster, rreg7_cluster, rreg8_cluster, type = "latex", keep = c("treatlowpost", "treatmedpost", "treathighpost"), header = FALSE, title = "Table A2: Panel B", dep.var.caption = "", column.labels = c("Output", "Attendance", "Output", "Attendance", "Output", "Attendance", "Output", "Attendance"), table.placement = "H",add.lines=list(c('Sample', 'Relevant', 'Relevant', 'Relevant', 'Relevant', 'Full','Full','Full','Full'), c('Pre-trmt obs','Yes','Yes','Yes','Yes','Yes','Yes','No','No'), c('Neighbor ctrls', 'No', 'No', 'Yes', 'Yes', 'Yes','Yes','Yes','Yes'), c('Individual FEs', 'Yes', 'Yes', 'Yes', 'Yes', 'Yes','Yes','No','No'), c('N','4,307','4,307','4,307','4,307','8,375','8.375','5,283','5,283')))
```

\bigskip
\noindent
Also note that the original replication code provided in Stata contained a minor error that caused the code to not replicate columns (7) and (8) in Table A.II. Specifically, the Globals "neighbor_pre_noT" and "neighbor_pre" were not defined in the original replication code but were supposed to be included in the specifications for (7) and (8). This replication code corrects this error and successfully replicates the original results reported Table A.II Columns (7) and (8) in the published Appendix. 

```{r Robustness Check, results = 'asis', echo = FALSE, fig.align = "center", out.width = 4, out.height = 4, warning = FALSE}
#===========================================================
# Robustness Checks: Allow for more flexible functional form 
#===========================================================

#Generate days_experience variable from available data
final[task_id == 1,days_experience := exper_task_lin1]
final[task_id == 3,days_experience := exper_task_lin3]
final[task_id == 4, days_experience := exper_task_lin4]
final[task_id == 5,days_experience := exper_task_lin5]
final[task_id == 6, days_experience := exper_task_lin6]
final[task_id == 8, days_experience := exper_task_lin8]
final[task_id == 9,days_experience := exper_task_lin9]
final[task_id == 10, days_experience := exper_task_lin10]
final[task_id == 11,days_experience := exper_task_lin11]
final[task_id == 12, days_experience := exper_task_lin12]

# Generate days_experience squared
final[,days_experience_sq := days_experience^2]

# Generate days_experience cubed
final[,days_experience_cb := days_experience^3]

#### Re-analyze Table IV including interaction terms between days_experience cubed and task_id dummies
### Panel A: Pooled Treatment Effects
## Without FE
x <- c("posttreat", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", "low_p", "med_p", "high_p", "treatlow", "treatmed", "treathigh", "irrellow", "irrelmed", "irrelhigh", "day_round", exper_task_lin, exper_task_sq, "task_id", neighbor_all)
x <- paste(x, collapse = "+")

# dependent variable = output
reg1_check <- lm(formula(paste0("prodnorm", "~",x,"+days_experience_cb*task_id")), data = final)
vcov_teamid <- cluster.vcov(reg1_check, final$team_id)
reg1_check_cluster <- coeftest(reg1_check, vcov_teamid)

# dependent variable = attendance
reg2_check <- lm(formula(paste0("attendance", "~", x,"+days_experience_cb*task_id")), data = final)
vcov_teamid <- cluster.vcov(reg2_check, final$team_id)
reg2_check_cluster <- coeftest(reg2_check, vcov_teamid)

# conditional on attendance - no FE
x <- c("posttreat", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", "low_p", "med_p", "high_p", "treatlow", "treatmed", "treathigh", "irrellow", "irrelmed", "irrelhigh", "day_round", exper_task_lin, exper_task_sq, "task_id", neighbor_all)
x <- paste(x, collapse = "+")

reg5_check <- lm(formula(paste0("prodnorm", "~", x, "+days_experience_cb*task_id")), data=final[attendance == 1,])
vcov_teamid <- cluster.vcov(reg5_check, final[attendance == 1, team_id])
reg5_check_cluster <- coeftest(reg5_check, vcov_teamid)

# combine models into latex table
stargazer(reg1_cluster, reg1_check_cluster, reg2_cluster, reg2_check_cluster, reg5_cluster, reg5_check_cluster, type = "latex", keep = "posttreat", header = FALSE, title = "Table 4 Panel A Robustness Check: Include experience cubed controls", dep.var.caption = "", column.labels = c("Output", "Output", "Attendance", "Attendance", "Output|Att", "Output|Att"), table.placement = "H",add.lines = list(c('Exper Cubed Controls','No','Yes', 'No', 'Yes', 'No', 'Yes'), c('Individual Fixed effects', 'No', 'No', 'Yes', 'Yes', 'No','No'), c('N','8,375','8,375','8,375','8,375','7,678','7,678')))

### Panel B: Treatment Effects Separately by Rank
## Without FE
x <- c("treatlowpost", "treatmedpost", "treathighpost", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", "low_p", "med_p", "high_p", "treatlow", "treatmed", "treathigh", "irrellow", "irrelmed", "irrelhigh", "day_round", exper_task_lin, exper_task_sq, "task_id", neighbor_all)
x <- paste(x, collapse = "+")

# dependent variable = output
reg6_check <- lm(formula(paste0("prodnorm", "~",x, "+days_experience_cb*task_id")), data = final)
vcov_teamid <- cluster.vcov(reg6_check, final$team_id)
reg6_check_cluster <- coeftest(reg6_check, vcov_teamid)

# dependent variable = attendance
reg7_check <- lm(formula(paste0("attendance", "~",x,"+days_experience_cb*task_id")), data = final)
vcov_teamid <- cluster.vcov(reg7_check, final$team_id)
reg7_check_cluster <- coeftest(reg7_check, vcov_teamid)

# conditional on attendance - no FE
x <- c("treatlowpost", "treatmedpost", "treathighpost", "lowpost", "medpost", "highpost", "irrelpostlow", "irrelpostmed", "irrelposthigh", "low_p", "med_p", "high_p", "treatlow", "treatmed", "treathigh", "irrellow", "irrelmed", "irrelhigh", "day_round", exper_task_lin, exper_task_sq, "task_id", neighbor_all)
x <- paste(x, collapse = "+")

reg10_check <- lm(formula(paste0("prodnorm", "~", x, "+days_experience_cb*task_id")), data=final[attendance == 1,])
vcov_teamid <- cluster.vcov(reg10_check, final[attendance == 1, team_id])
reg10_check_cluster <- coeftest(reg10_check, vcov_teamid)

# combine models into latex table
stargazer(reg6_cluster, reg6_check_cluster, reg7_cluster, reg7_check_cluster, reg10_cluster, reg10_check_cluster, type = "latex", keep = c("treatlowpost", "treatmedpost", "treathighpost"), header = FALSE, title = "Table 4 Panel B Robustness Check: Include experience cubed controls", dep.var.caption = "", column.labels = c("Output", "Output", "Attendance", "Attendance", "Output|Att", "Output|Att"), table.placement = "H",add.lines = list(c('Exper Cubed Controls','No','Yes', 'No', 'Yes', 'No', 'Yes'), c('Individual Fixed effects', 'No', 'No', 'Yes', 'Yes', 'No','No'), c('N','8,375','8,375','8,375','8,375','7,678','7,678')))
```

As a robustness check, I test the sensitivity of the main results on the effects of pay disparity to functional form assumptions. In the original specification, the authors include controls with both experience and the square of experience to allow for task-specific non-linearities in returns to experience. However, the choice to include only experience and experience squared terms, rather than higher order terms, is arbitrary and imposes implicit functional form assumptions. I test the sensitivity of the original results to functional form assumptions by re-analyzing Table IV including controls with experience cubed interacted with task dummies. Note that this change is only relevant for the specifications that do not include individual fixed effects. 

\bigskip
\noindent
The results from this variation are very similar to the original results, suggesting that the original results are not driven by functional form assumptions. 